Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-30 analysis/presentation/sim_survey_presentation.Rmd
Add new truth vs estimate plots to presentation

## Age strat

### Some results

<dev class = "left">
```{r}
plot_age_strat_fan(sim, surveys = 1:5, 
                   plot_bgcolor = "transparent",
                   paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

>>>>

## Truth vs. estimate

### Total abundance

<dev class = "left">
```{r}
plot_total_strat_fan(sim, surveys = 1:5, 
                     plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                     font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

## Truth vs. estimate

### Abundance at age

<dev class = "left">
```{r}
surveys <- sim$surveys[set_den %in% c(0.0005, 0.001, 0.002, 0.01) &
                         lengths_cap %in% c(10, 100, 500, 1000) &
                         ages_cap %in% c(5, 10, 50), ]
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   years = 1:5, ages = sim$ages, select_by = "year",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>

## Truth vs. estimate

### Abundance at age

<dev class = "left">
```{r}
plot_age_strat_fan(sim, surveys = surveys$survey, 
                   ages = 2:6, years = sim$years, select_by = "age",
                   plot_bgcolor = "transparent", paper_bgcolor = "transparent",
                   font = list(size = 14, family = "'Montserrat', sans-serif"))
```
</dev>
